\documentclass[a4paper,twoside]{article}

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.


\usepackage{comment}

\subfigtopskip=0pt
\subfigcapskip=0pt
\subfigbottomskip=0pt

\usepackage{graphicx}
% to typeset algorithms
%\usepackage{algorithmic}
\usepackage{algorithm}
% to typeset code fragments
\usepackage{listings}
% to make an accent \k be available
\usepackage[OT4,T1]{fontenc}
% provides various features to facilitate writing math formulas and to improve the typographical quality of their output.
%\usepackage[cmex10]{amsmath}
%\interdisplaylinepenalty=2500
% por urls typesetting and breaking
\usepackage{url}
% for vertical merging table cells
\usepackage{multirow}

\usepackage{filecontents}

\usepackage{multicol}
\usepackage{lipsum}
\usepackage{color}
\usepackage{xcolor}
\usepackage{colortbl}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{BluishGray}{RGB}{226,227,231}
\definecolor{LightGray}{gray}{0.95}
\definecolor{Gray}{gray}{0.85}
\usepackage{algpseudocode,algorithmicx}
\usepackage{comment}
\newcommand*\DNA{\textsc{dna}}

\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmicx}

%\parskip=0.2\baselineskip

\usepackage{booktabs}% http://ctan.org/pkg/booktabs
\newcommand{\tabitem}{~~\llap{\textbullet}~~}



\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}



% define environments for remarks and examples
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}
\newcommand{\ti}{\textit}
\newcommand{\tb}{\textbf}
\newcommand{\tf}{\textsf}
\newcommand{\ttt}{\textit}
\usepackage{mathtools}

\usepackage{cuted}\usepackage{mathtools}

\usepackage{cuted}
\newcounter{mytempeqncnt}

\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{framed}
\usepackage[listings,skins]{tcolorbox}
\usepackage[skipbelow=\topskip,skipabove=\topskip]{mdframed}
\mdfsetup{roundcorner=0}

\usepackage[normalem]{ulem}

\usepackage{alltt}


%to change to spacing between floats (figures) and text
\setlength{\textfloatsep}{2pt plus 1.0pt minus 2.0pt}



\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
	backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
	basicstyle=\tiny,        % the size of the fonts that are used for the code
	lineskip={-1.5pt},
	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
	breaklines=true,                 % sets automatic line breaking
	captionpos=t,                    % sets the caption-position to bottom
	commentstyle=\color{mygreen},    % comment style
	deletekeywords={...},            % if you want to delete keywords from the given language
	escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
	extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
	frame=single,	                   % adds a frame around the code
	keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
	keywordstyle=\textbf,       % keyword style
	language=Octave,                 % the language of the code
	otherkeywords={*,state, shallow,history,final,transition,table,initial,machine,transition,choice,exit,point,entry...},           % if you want to add more keywords to the set
	numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
	numbersep=5pt,                   % how far the line-numbers are from the code
	numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
	rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
	showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
	showstringspaces=false,          % underline spaces within strings only
	showtabs=false,                  % show tabs within strings adding particular underscores
	stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
	frame=none,
	stringstyle=\color{mymauve},     % string literal style
	tabsize=2,	                   % sets default tabsize to 2 spaces
	title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\begin{document}

\title{RAOES: Round-trip Engineering for Event-Driven Embedded System Development and Evolution}

\author{%\authorname{First Author Name\sup{1}, Second Author Name\sup{1} and Third Author Name\sup{2}}
%\affiliation{\sup{1}Institute of Problem Solving, XYZ University, My Street, MyTown, MyCountry}
%\affiliation{\sup{2}Department of Computing, Main University, MySecondTown, MyCountry}
%\email{\{f\_author, s\_author\}@ips.xyz.edu, t\_author@dc.mu.edu}
}

\keywords{To be added}

\abstract{A UML State Machine and its visualizations are efficient to model the logical behavior of event-driven embedded systems.   
	Model Driven Engineering generates executable code from state machines. 
	The generated code can then be modified by programmers.
	Round-trip engineering is a technique used to propagate changes made in the code to the original model.
	However, existing round-trip engineering tools and approaches mainly focus on structural parts of the system model such as those available from UML class diagrams.
	This paper tackles the problem of collaboration between software architects and programmers in developing event-driven embedded systems using UML State Machine to describe the behavior.
	We propose RAOES-a round-trip engineering and synchronization of model and code, with which the software architects and programmers can freely switch between model and code to be efficient with their preferred practice.
	To do it, RAOES proposes to generate an intermediate representation, which acts as a bridge to connect the code to the model.
	We implemented a prototype and conducted experiments to evaluate RAOES.}

\onecolumn \maketitle \normalsize \vfill

\input{sections/introduction}

%\input{sections/background}

\input{sections/motivation}

\input{sections/overview}

\input{sections/syntax}

\input{sections/synchronization}

%\input{sections/codegentex}

\input{sections/implementation}

\input{sections/experiment}

%\input{sections/casestudy}

%\input{sections/evaluationplan}

\input{sections/relatedwork}

%\input{sections/discussion}

\input{sections/conclusion}

\section*{\uppercase{Acknowledgements}}

\noindent If any, should be placed before the references section
without numbering. To do so please use the following command:
\textit{$\backslash$section*\{ACKNOWLEDGEMENTS\}}


\vfill
\bibliographystyle{apalike}
{\small
\bibliography{refs}}


\section*{\uppercase{Appendix}}

\noindent If any, the appendix should appear directly after the
references without numbering, and not on a new page. To do so please use the following command:
\textit{$\backslash$section*\{APPENDIX\}}

\vfill
\end{document}

