\subsection{Model-Driven Round-trip Engineering}
\label{subsec:mdrtebackground}

In this section we define the actors who will use our model-code synchronization approach to collaborate during development.
%Then we define the main capabilities, as use-cases, expected from a generic IDE used by these actors.
Some basic concepts related to the actors and use-cases are also defined in this section.


%\subsection{Collaborating actors and development artifacts}

%In this paper we propose a methodological model-code synchronization pattern for collaboration between software
%architects and programmers.

%First, we introduce the concepts of \textit{development artifact} and \textit{baseline artifact}.

%\begin{definition}[Development artifact]
%	A development artifact is an artifact, as defined in \cite{omg_software_2008},
%	that can be used for the full implementation of the system.
%\end{definition}

%For example a system can be entirely implemented as code.
%Implementation code is a development artifact, so may model.
%It is then not only documentation of specification
%but part of the implementation.
%For example a model can be used for implementation by generating code from the model, and compiling the code without the need to edit or complete the code.
%In our work, we assume that model and code are both development artifacts.
%A development artifact may be the baseline artifact, defined in this paper as follows:

\begin{comment}

\begin{definition}[Baseline artifact]
	A baseline artifact is one which may be edited manually.
	All other artifacts are produced from the baseline artifact
	through some process, and only through a process. Manual edition
	of artifacts other than the baseline artifact is forbidden.
\end{definition}
\end{comment}

Two primary actors, called \ttt{model-driven developer}
and \ttt{code-driven developer}, are introduced.
%The main difference between them
%is what they consider as the baseline artifact.

\begin{definition}[Model-driven developer]
	A model-driven developer (MDD) is an actor in a software development process and uses the model as the main working artifact.
\end{definition}

%In other words, for the model-driven developer only the model should be edited manually. 
The code must always be produced from the model automatically
by some process that guarantees that the code is consistent with the model.
A software architect is a kind of the model-driven developer
who edits the model to specify the architecture of the system.
%An architect presumes that the reference for the architecture
%of the system should be specified as a model.

\begin{definition}[Code-driven developer]
	Code-driven developer (CDD) is an actor who uses the code as the main working artifact.
\end{definition}

A programmer is a specialization of the code-driven developer.
Indeed, programmers may modify our C++ front-end code, such as editing methods, attributes or state machines textually.
%The code is then the main reference for the implementation of methods.

%There are some use-cases for manual edition of artifacts. The \texttt{Edit Artifact} use-case
%implies that the IDE must have some tool to let the developer manually edit an artifact.
%The \texttt{Edit Model} and \texttt{Edit Code} use-cases are specializations of the \texttt{Edit Artifact}
%use-case where the artifact is the model or code.

%There are also some use-cases related to the synchronization of artifacts. The \texttt{Synchronize Artifact} use-case (1) compares two artifacts, (2) updates each with editions made
%in the related artifact, and (3) reconciles conflicts when appropriate. The \texttt{Synchronize Model} and \texttt{Synchronize Code}
%use-cases are specializations where, respectively, the model or the code are the artifacts being synchronized.

\texttt{Generate Code} is a use-case related to forward engineering.
It is the production of C++ code from a model.
The developer can either use \texttt{Generate Code (Batch)} or \texttt{Generate Code (Incremental)}.
%\end{comment}

\begin{definition}[Batch code generation \cite{Giese2006}]
	Batch code generation is a process of generating code
	from a model, from scratch.
	Any existing code is overwritten by the newly generated code.
\end{definition}

\ttt{Incremental code generation} is a specialization of \ttt{incremental model transformation}, which
does not generate the whole target model from scratch but only updates the target model by
propagating editions made to the source model.

%\texttt{Incremental code generation (ICG)} \ti{$gen_{inc}$ is a process of taking as input a changed model m and an existing executable code to make the code synchronized with the changed model: $gen_{inc}(m, c) = c'$. Non-conflicted changes at the code side are kept intact the synchronization. ICG is also defined as a process of taking model changes ch and an existing code c: $gen_{inc}(ch, c) = c'$}.

%Derived from the definition of incremental model transformation, 
%Incremental code generation
%is defined in this paper as follows:

\begin{definition}[Incremental code generation]
	Incremental code generation is the process
	of taking as input an edited model, and existing code, and then updating the code by propagating
	editions in the model to the code.
\end{definition}

%\begin{comment}
\texttt{Reverse Code} is related to reverse engineering.
\texttt{Reverse Code} is the production of a model, in a modeling language such as UML, from code, written in a programming language.
The developer can either use \texttt{Reverse Code (Batch)} or \texttt{Reverse Code (Incremental)}, which are defined in this paper as follows:
%\end{comment}

\begin{definition}[Batch reverse engineering]
	Batch reverse engineering is a process of producing a model from code, from scratch.
	The existing model is overwritten by the newly produced model.
\end{definition}

\begin{definition}[Incremental reverse engineering]
	Incremental reverse engineering is the process of taking as
	input a edited code, and an existing model, and then updating the model by propagating
	editions in the code to the model.
\end{definition}

%For readability, in this paper we will sometimes designate batch and incremental as modes
%of code generation/reverse; e.g. we say that we generate code in batch mode from a model.

%The use-cases are generic. They do not depend
%on any particular approach or tool. Therefore the software developers
%can choose the approach or tool that suits better his/her
%development preferences best.

In Section \ref{sec:collaboration}, the use-cases of the IDE are integrated into
our process, which covers model-code synchronization and is detailed in Section \ref{sec:collaboration}.
%The scenarios correspond to behaviors performed by both kinds of actors,
%i.e. model-driven developers and code-driven developers.

%Model-driven engineering has been established as a potential approach to gain software quality and productivity \cite{Mussbacher2014}. 